StreamReduce: A Data Stream Processor with MapReduce Parallelism

### 2012-05-15 paper/paper.tex
More edits

\subsection{Precision and Recall}
StreamReduce transforms some input into a result. The transformation is affected by
the substitution transformations and descisions to kill tasks that workers make.
The result of a StreamReduce computation is sensitive to the properties of the input
and the the properties of the transformation applied.

Every data set has some base level of noise in it due to such things as how the data is
sampled. StreamReduce introduces another source of noise by discarding data and
substituting computation algorithms. Certain combinations of inputs and transformations
may be able to withstand this additional noise while other combinations of inputs and
transformations may not.

@@

\subsubsection{Precision}
For the results given by StreamReduce's top-k computation to be meaningful,
it is important for the distribution of the top-k words to be resistant to perturbations,
which implies that task killing minimally impacts the head of the word distribution.
Table~\ref{table:top10} shows the top-10 words and their frequencies. Within the true top-10
words, the first word occurs twice as often as the tenth word, and the difference in frequencies
of adjacently ranked words varies from~400--4000. Given that the data set has approximately~16 million
words and~3500 articles, there are about~4500 words in any given article. Even the most frequently
occuring word only appears on average~8 times per article.
%Gaps in the hundreds are stable in the
%addition or removal of tens of articles.

Table~\ref{table:top10} and Figure~\ref{fig:precision} show that the Wikipedia
data set has sufficient spacing in the head of its distribution to withstand the
data-discarding transformations that StreamReduce employs.

Figure~\ref{fig:precision} shows that even with a task kill rate of~0.8 and a work level of~0.4,
meaning that the cluster only looks at 8\% of the words in the corpus, the results
are at least~80\% accurate. Increasing the work level, which increases the fidelity of
results emitted by workers, also increases the fidelity of the top~100 results.

>>>>

\subsection{Precision and Recall}
StreamReduce transforms some input into a result. The transformation is affected by
the substitution transformations and descisions to kill tasks that workers make.
The result of a StreamReduce computation may be affected by the properties of the input
and the properties of the transformation applied.

Every data set has some base level of noise in it due to such things as how the data is
sampled. StreamReduce introduces another source of noise by discarding data and
substituting computation algorithms. For certain combinations of inputs and transformations,
this additional noise may have very little impact on the result
while for other combinations, the impact may be larger.

@@

\subsubsection{Precision}
For the results given by StreamReduce's top-k computation to be meaningful,
it is important for the distribution of the top-k words to be resistant to perturbations,
which implies that task killing minimally impacts the head of the word distribution.
Table~\ref{table:top10} shows the top-10 words and their frequencies. Within the true top-10
words, the first word occurs twice as often as the tenth word, and the difference in frequencies
of adjacently ranked words varies from~400--4000. Given that the data set has approximately~16 million
words and~3500 articles, there are about~4500 words in any given article. Even the most frequently
occuring word only appears on average~8 times per article.

This significant spacing in the top~100 words makes it likely that the input will produce an
accurate result when StreamReduce transforms it by discarding data.

Table~\ref{table:top10} and Figure~\ref{fig:precision} show that the Wikipedia
data set has sufficient spacing in the head of its distribution to withstand the
data-discarding transformations that StreamReduce employs. The top~100 always includes at
least~86 of the top~100 words and in most cases includes more than~90 of the top~100.

Figure~\ref{fig:precision} shows that even when the input is processed by a transformation that deviates
from perfect-fidelity, StremReduce still returns meaningful results.
When transforming the input with a task kill rate of~0.8 and a work level of~0.4,
meaning that the cluster only looks at~8\% of the words in the corpus, the results
are at least~80\% accurate. Increasing the work level, which increases the fidelity of
results emitted by workers, also increases the fidelity of the top~100 results.
